---
title: "Phone Analysis"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

This is a Phone Analysis Conducted in Ghana.

```{r}
#loading the required package needed for the analysis.
library(tidyverse)

```
```{r}
Mobile_phone <- read.csv("../mobile phone EDA/Mobile-Phones.csv")
head(Mobile_phone)
Mobile_phone1 <- Mobile_phone |> 
  rename(price = price...)
```

 Exploring the most Expensive Phones.
```{r}
#Find the most expensive phones 

Most_Expensive <- Mobile_phone1 |>
  select (os,  brand,model, price, resolution, battery.mAh. ) |>
  group_by(price) |> 
  arrange(desc(price)) |> 
  head(10)
Most_Expensive
```
Unsurprisingly, Apple and Samsung have the most expensive phones.


A bit of Data Wrangling. 
Renaming IOS to iOS and Windows to Windows Phone.
```{r}
Mobile_phone1$os <- ifelse(Mobile_phone1$os == "IOS", "iOS", 
         ifelse(Mobile_phone1$os == "Windows", "Windows Mobile",
                ifelse(Mobile_phone1$os == "", "Unknown", Mobile_phone1$os)))
```
Checking.....
```{r}
ggplot(Mobile_phone1, aes(x = os, y = price)) + geom_point(aes(color = os))
```

Renaming all empty rows in the data to Unknown
```{r}
# Renaming all empty rows in the data set to Unknown.
Mobile_phone1 <- Mobile_phone1 |>
  mutate(across(everything(), ~ifelse(.=="", "Unknown",.)))

head(Mobile_phone1)
```

Galaxy Z Fold 4 came without Battery Capacity. Manual Insertion had to be done.
```{r}
#Inserting Battery.mAh. for Galaxy Z fold 4
Mobile_phone1 <- Mobile_phone1 |>
  mutate(battery.mAh. = ifelse(model == "Galaxy Z Fold4",4400, battery.mAh. ))

Mobile_phone1 |> select(brand, battery.mAh., model) |>
  filter( model == "Galaxy Z Fold4")
```

Regional Analysis of Phones with Graphics
```{r}
Region_data <- Mobile_phone1 |> 
  select(region, location) |> 
  group_by(region)  |>
  count()
Region_data

Region_data <- Mobile_phone1 |> 
  select(region, location) |> 
  group_by(region, location) |>
  count()
 Region_data
#graphics of phone by region
ggplot(Region_data, aes(x = region )) + geom_bar(aes( fill = region)) + 
  ylab("Total number of phones ")+  labs(title = "Phones by Region")
```
```{r}
#faceting  brand by region 
ggplot(Mobile_phone1, aes( x= brand)) + geom_bar(aes(fill = brand, )) + facet_grid(~ region) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```
Exploring Devices with the highest Battery Capacity
```{r}
#Highest battery capacity  phones
Mobile_phone1 |>
  select(brand, model, battery.mAh., resolution) |>
  arrange(desc(battery.mAh.)) |>
  head(5) 
```
Now we delve with devices with the lowest battery Capacity.
```{r}
Mobile_phone1 |>
  select(brand, model, battery.mAh., resolution ) |>
  arrange(desc(battery.mAh.)) |>
  na.omit(battery.mAh.) |>
  tail(5) 
```
```{r}
#Average Price of the Phones 
android_avg <- Mobile_phone1 |>
  select(os,price)|>
  filter(os == 'Android') |>
   mutate( mean(price)) |>
  head(1)

iOS_avg <- Mobile_phone1 |>
  select(os,price)|>
  filter(os == 'iOS') |>
  mutate( mean(price)) |>
  head(1)


iOS_avg
android_avg

avg_means = data.frame(iOS_avg, android_avg)
avg_means

 

```

