---
title: "Phone Analysis"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

This is a Phone Analysis Conducted in Ghana.

```{r}
#loading the required package needed for the analysis.
library(tidyverse)

```
```{r}
Mobile_phone <- read.csv("../mobile phone EDA/Mobile-Phones.csv")
head(Mobile_phone)
Mobile_phone1 <- Mobile_phone |> 
  rename(price = price...)
```

 Exploring the most Expensive Phones.
```{r}
#Find the most expensive phones 

Most_Expensive <- Mobile_phone1 |>
  select (os,  brand,model, price, resolution, battery.mAh. ) |>
  group_by(price) |> 
  arrange(desc(price)) |> 
  head(10)
Most_Expensive
```
Unsurprisingly, Apple and Samsung have the most expensive phones.


A bit of Data Wrangling. 
Renaming IOS to iOS and Windows to Windows Phone.
```{r}
Mobile_phone1$os <- ifelse(Mobile_phone1$os == "IOS", "iOS", 
         ifelse(Mobile_phone1$os == "Windows", "Windows Mobile",
                ifelse(Mobile_phone1$os == "", "Unknown", Mobile_phone1$os)))
```
Checking.....
```{r}
ggplot(Mobile_phone1, aes(x = os, y = price)) + geom_point(aes(color = os))
```

Renaming all empty rows in the data to Unknown
```{r}
# Renaming all empty rows in the data set to Unknown.
Mobile_phone1 <- Mobile_phone1 |>
  mutate(across(everything(), ~ifelse(.=="", "Unknown",.)))

head(Mobile_phone1)
```

Galaxy Z Fold 4 came without Battery Capacity. Manual Insertion had to be done.
```{r}
#Inserting Battery.mAh. for Galaxy Z fold 4
Mobile_phone1 <- Mobile_phone1 |>
  mutate(battery.mAh. = ifelse(model == "Galaxy Z Fold4",4400, battery.mAh. ))

Mobile_phone1 |> select(brand, battery.mAh., model) |>
  filter( model == "Galaxy Z Fold4")
```

Regional Analysis of Phones with Graphics
```{r}
Region_data <- Mobile_phone1 |> 
  select(region, location) |> 
  group_by(region)  |>
  count()
Region_data

Region_data <- Mobile_phone1 |> 
  select(region, location) |> 
  group_by(region, location) |>
  count()
 Region_data
#graphics of phone by region
ggplot(Region_data, aes(x = region )) + geom_bar(aes( fill = region)) + 
  ylab("Total number of phones ")+  labs(title = "Phones by Region")
```

